Visualizations for article

### 2016-05-26 101-visualizations-for-article.Rmd
Changes to NA color plus new spectrograms

```{r}
spectrogram("CO1868", best_matches, white_list = 8)
```

>>>>

```{r}
spectrogram("CO1868", best_matches, white_list = c("IL1866", "IN1843", "IA1839"))
```

CO1877: companion visualization of Colorado under the Field code

```{r}
spectrogram("CO1877", best_matches, white_list = 8) 
```

MT 1895

```{r}
spectrogram("MT1895", best_matches, white_list = 8)
```
